State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-06-11 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
some editions

\section{Results}\label{ResultsSection} The non-reduced neural field model derived in Section~\ref{NeuralModelSection} was used to generate the data for state and parameter estimation. All parameters for the model are given in Table~\ref{tab:Model Parameters}. Figure~\ref{fig:experimental design}(b) shows example data from the sensors of the model, and figure~\ref{fig:experimental design}(c) shows the power spectral density (PSD) of the simulated time-series. The PSD shows the typical $1/f^2$ characteristics of intracranial EEG.

@@

\end{tabular}\label{tab:Model Parameters}

@@

@@

\begin{figure}[th]\label{fig:experimental design}

@@

>>>>

\section{Results}\label{ResultsSection} The non-reduced neural field model derived in Section~\ref{NeuralModelSection} was used to generate the data for state and parameter estimation. All parameters for the model are given in Table~\ref{tab:Model Parameters}. Figure~\ref{fig:experimental design}(a) shows example data from the sensors of the model, and figure~\ref{fig:experimental design}(b) shows the power spectral density (PSD) of the simulated time-series. The PSD shows the typical $1/f^2$ characteristics of intracranial EEG.

@@

\end{tabular}

@@

\label{tab:Model Parameters}

@@

@@

\label{fig:experimental design}
